
# (PART) 💡 SOLUTIONS {-}

```{r include=FALSE}
knitr::opts_chunk$set(fig.pos = "!H", out.extra = "")
```

# Chapter 1 {- #ch1}

## Exercise 1.1 {- #q1.1}

### Q1 {- #q1.1.1}
(Fernando Li)

(a) $$ A \cap B = \lbrace 2,3,5,7 \rbrace $$
(b) $$ A \cap C = \lbrace 2,4,6,8,10 \rbrace $$
(c) $$ B \cap C = \lbrace 2 \rbrace $$
(d) $$ A \cup B = \lbrace 1,2,3,4,5,6,7,8,9,10,11,13,17,19 \rbrace $$
(e) $$ A \cup C = \lbrace 1,2,3,4,5,6,7,8,9,10,12,14,16,18 \rbrace $$
(f) $$ B \cup C = \lbrace 2,3,4,5,6,7,8,10,11,12,13,14,16,17,18,19 \rbrace $$
(g) $$ A \cup B \cup C = \lbrace 1,2,3,4,5,6,7,8,9,10,11,12,13,14,16,17,18,19 \rbrace $$
(h) $$ A \cap B \cap C = \lbrace 2 \rbrace $$
(i) $$ (A \cup B) \cap C = \lbrace 2,4,6,8,10 \rbrace $$
(j) $$ (A \cap B) \cup C = \lbrace 2,3,4,5,6,7,8,10,12,14,16,18 \rbrace $$
(k) $$ A \cap B' = \lbrace 1,4,6,8,9,10 \rbrace $$
(l) $$ 'A \cap B' = \lbrace 12,14,15,16,18 \rbrace $$

### Q2 {- #q1.1.2}
(David Rosa)

(a)false, a counterexample is as follows
$$ A = \lbrace 1,2,3,4 \rbrace \\
   B = \lbrace 3,4,5,6 \rbrace \\
   U = \lbrace 1,2,3,4,5,6,7,8 \rbrace \\$$
Then $$ A - B = \lbrace 1,2 \rbrace \\
        A' = \lbrace 5,6,7,8 \rbrace \\
        A' \cap B = \lbrace 5,6 \rbrace \\$$
Thus $$ A - B = A' \cap B $$ is false.

(b)false, a counterexample is as follows
$$ A = \lbrace 1,2 \rbrace \\
   B = \lbrace 2,3 \rbrace \\
   C = \lbrace 3,4 \rbrace \\
   U = \lbrace 1,2,3,4,5 \rbrace \\$$
Then $$ A \cup B = \lbrace 1,2,3 \rbrace \\
        (A \cup B) \cap C = \lbrace 3 \rbrace \\
        B \cap C = \lbrace 3 \rbrace \\
        A \cup ( B \cap C) = \lbrace 1,2,3 \rbrace \\ $$
Thus $$ (A \cup B) \cap C = A \cup ( B \cap C) $$ is false.

(c)true
As $$ B' \cap B = \emptyset $$
$$ (A' \cup B') \cap B = (A' \cap B) \cup (B' \cap B) \\
= (A' \cap B) \cup \emptyset \\
= A' \cap B \\
= \lbrace x \in U : x \in B \ and \ x \in A' \rbrace\\
= \lbrace x \in U : x \in B \ and \ x \notin A \rbrace\\
= B -A $$

## Exercise 1.2 {- #q1.2}

### Q1 {- #q1.2.1} 

(a) $$ \lbrace x:\pm \sqrt2 \rbrace $$
(b) $$ \lbrace x: \sqrt2 \rbrace $$
(c)Q means rational numbers, so $$\lbrace x \in Q: x^2 = 2 \rbrace =  \emptyset $$

### Q2 {- #q1.2.2} 
(Jiin Kim)

(a)$$ A \cap B = [3,5]  $$
(b)$$ A \cup B = [1,9)  $$
(c)$$ A - C = (1,5)  $$
(d)$$ B \cap C = \lbrace 5 \rbrace  $$
(e)$$ C - B = \lbrace 1 \rbrace  $$
(f)$$ B - C = [3,5) \cup (5,9) $$
(g)$$ B - (B - C) = \lbrace 5 \rbrace $$
(h)$$ A \cup D = [1,\infty)  $$
(i)$$ C \cap D = \lbrace 5 \rbrace  $$

## Exercise 1.3 {- #q1.3}

### Q1 {- #q1.3.1}
(Maria Kahlert)

(a)$$ 2x-3 \geq 4+7x \\
      2x-7x \geq 4+3 \\
      -5x \geq 7 \\
      x \leq -\frac{7}{5}$$

(b)$$ 8(x+1)-2 < 5(x-6)+7 \\
      8x+8-2 < 5x-30+7 \\
      3x < -29 \\
      x < -\frac{29}{3}$$

(c)As $$ x^2+1 > 0 $$
$$ \frac{x^2-3x+7}{x^2+1} < 1 \\
      x^2-3x+7 < x^2+1  \\
      -3x < -6 \\
      x > 2$$
(d)$$ (2x+7)(5-11x) \leq 0 \\
      (x+\frac{7}{2})(x - \frac{5}{11}) \geq 0 \\
      x \geq \frac{5}{11} \ or\  x \leq -\frac{7}{2}$$

(e)$$ (x^2-2x-3) <0 \\
      (x-3)(x+1) <0 \\
      -1<x<3$$
(f)$$ 2x^2-3x > 4 \\
      2x^2-3x-4 > 0 $$
When $$ 2x^2-3x-4 = 0 $$
$$ x = \frac{-(-3) \pm \sqrt{[(-3)^2-4\times2\times(-4)]} }{2\times2}\\
     = \frac{3 \pm \sqrt{41} }{4}$$
Thus $$ 2x^2-3x-4 > 0 \\
  x < \frac{3 - \sqrt{41} }{4} \ or \ x > \frac{3 + \sqrt{41} }{4}$$

(g)$$ 2x^2-3x < -4 \\
      2x^2-3x+4 < 0 $$
When $$ 2x^2-3x+4 = 0 $$
$$ (-3)^2-4\times2\times4 = -23 <0 $$
Thus the equation has no solution.
Thus $$ 2x^2-3x+4 < 0 \\
  x \in \emptyset $$
(h)$$ \frac{2x+3}{x-4} \geq 0 \\
      (2x+3)(x-4) \geq 0 \ and\  x \neq 4 \\
      (x+\frac{3}{2})(x-4) \geq 0 \ and\  x \neq 4 \\
      x > 4 \ or \  x \leq -\frac{3}{2}$$
(i)$$ \frac{2x+3}{x-4} < 1 \\
\frac{2x+3}{x-4} -1 <0 \\
\frac{2x+3}{x-4} - \frac{x-4}{x-4} <0\\
\frac{x+7}{x-4} < 0 \\
      (x+7)(x-4) < 0 \\
      -7<x<4$$

### Q2 {- #q1.3.2}

(a)$$ 2x^3+7x^2-15x = x(2x^2+7x-15) \\
                    = x(x+5)(2x-3)$$
(b)$$ 2x^3+3x^2-2x-3 = (2x^3-2x)+(3x^2-3) \\
                     = 2x(x^2-1) + 3(x^2-1) \\
                     = (2x+3)(x^2-1) \\
                     = (2x+3)(x+1)(x-1)$$
(c)$$ x^3-x^2-x-2 = (x^3-1)-(x^2+x+1) \\
                  = (x-1)(x^2+x+1)-(x^2+x1) \\
                  = (x-1-1)(x^2+x+1) \\
                  = (x-2)(x^2+x+1)$$
(d)$$ x^4-3x^3-13x^2+15x = x(x^3-3x^2-13x+15) \\
                         = x[(x^3-x)+(-3x^2-12x+15)] \\
                         = x[x(x^2-1)-3(x^2+4x-5)] \\
                         = x[x(x+1)(x-1)-3(x-1)(x+5)] \\
                         = x(x-1)[x(x+1)-3(x+5)] \\
                         = x(x-1)(x^2-2x-15)\\
                         = x(x-1)(x+3)(x-5)$$
(e)$$ x^4-3x^3+x^2+3x-2 = (x^4+x^2-2)+(-3x^3+3x) \\
= (x^2+2)(x^2-1)-3x(x^2-1) \\
= (x^2+2-3x)(x^2-1) \\
= [(x-2)(x-1)][(x+1)(x-1)] \\
= (x-2)(x+1)(x-1)^2$$

(f)$$  x^4-x^3+x^2-3x+2 = (x^4-x^3)+(x^2-3x+2) \\
= x^3(x-1)+(x-1)(x-2) \\
= (x-1)(x^3+x-2) \\
= (x-1)[(x^3-1)+(x-1)] \\
= (x-1)[(x-1)(x^2+x+1)+(x-1)] \\
= (x-1)^2(x^2+x+2)$$

### Q3 {- #q1.3.3}
(Ashley a-d; Byoungchurl Lee e-h)


(a)$$ (x-4)(9-5x)(2x+3) < 0 \\
      (x-4)(x-\frac{9}{5})(x+\frac{3}{2}) >0 \\
      x \in ( -\frac{3}{2},\frac{9}{5}) \cup (4, \infty)$$
(b)$$ (x-3)(2x+1)^2 \leq 0 \\
      (x-3)(x+\frac{1}{2})^2 \leq 0 \\
      x \in (-\infty, 3] $$
(c)$$ x^3-2x^2-5x+6 < 0 \\
      (x^3-x)+(-2x^2-4x+6) < 0\\
      x(x^2-1)-2(x^2+2x-3) < 0\\
      x(x-1)(x+1)-2(x+3)(x-1) < 0\\
      (x-1)[x(x+1)-2(x+3)] < 0 \\
      (x-1)(x^2-x-6) < 0 \\
      (x-1)(x-3)(x+2) <0 \\
      x \in (-\infty,-2) \cup (1,3) $$

(d)$$ -2x^3+x^2+15x-18 \leq 0 \\
      (-2x^3+8x)+(x^2+7x-18) \leq 0 \\
      -2x(x^2-4)+(x-2)(x+9) \leq 0 \\
      -2x(x+2)(x-2)+(x-2)(x+9) \leq 0 \\
      (x-2)[-2x(x+2)+(x+9)] \leq 0 \\
      (x-2)(-2x^2-3x+9) \leq 0 \\
      (x-2)(-2x+3)(x+3) \leq 0 \\
      (x-2)(x-\frac{3}{2})(x+3) \geq 0 \\
      x \in [-3,\frac{3}{2}] \cup [2,\infty)$$
(e)$$ x^3-x^2-5x-3 > 0 \\
      (x^3-x)+(-x^2-4x-3) > 0 \\
      x(x^2-1)-(x^2+4x+3) > 0 \\
      x(x-1)(x+1)-(x+3)(x+1) > 0 \\
      (x+1)[x(x-1)-(x+3)] > 0\\
      (x+1)(x^2-2x-3) > 0 \\
      (x+1)(x-3)(x+1) > 0 \\
      (x+1)^2(x-3) > 0 \\
      x \in (3,\infty)$$


(f)$$ x^3+3x^2+5x+3 \leq 0 \\
      (x^3-x)+(3x^2+6x+3) \leq 0 \\
      x(x^2-1)+3(x^2+2x+1) \leq 0 \\
      x(x-1)(x+1)+3(x+1)^2 \leq 0 \\
      (x+1)[x(x-1)+3(x+1)] \leq 0 \\
      (x+1)(x^2+2x+3) \leq 0 \\
      $$
As $$ x^2+2x+3 = (x^2+2x+1)+2 = (x+1)^2+2 > 0 $$
Thus $$ x^3+3x^2+5x+3=(x+1)(x^2+2x+3) \leq 0 \\
      x \in (-\infty,-1] $$
      
      
(g)$$ x^4+2x^3-13x^2-14x+24 > 0 \\
      (x^4+2x^3-3x^2)+(-10x^2-14x+24) > 0 \\
      x^2(x^2+2x-3)-2(5x^2+7x-12) > 0 \\
      x^2(x+3)(x-1)-2(x-1)(5x+12) > 0 \\
      (x-1)[x^2(x+3)-2(5x+12)] > 0 \\
      (x-1)(x^3+3x^2-10x-24) > 0 \\
      (x-1)[(x^3+3x^2+2x)+(-12x-24) >0\\
      (x-1)[x(x^2+3x+2)-12(x+2)]>0\\
      (x-1)[x(x+1)(x+2)-12(x+2)]>0\\
      (x-1)(x+2)[x(x+1)-12]>0\\
      (x-1)(x+2)(x^2+x-12) > 0\\
      (x-1)(x+2)(x+4)(x-3) > 0\\
      x \in (-\infty,-4) \cup (-2,1) \cup (3,\infty)$$
(h)$$ 6x^4+x^3-15x^2 \leq 0 \\
      x^2(6x^2+x-15) \leq 0 \\
      x^2(2x-3)(3x+5) \leq 0 \\
      x \in [-\frac{5}{3},\frac{3}{2}]$$

# Chapter 2 {- #ch2}

## Exercise 2.1 {- #q2.1}
()

## Exercise 2.2 {- #q2.2}

### Q1 {- #q2.2.1}
(Trang-Paige Tran a,c,e,g)

(a)$$ dom(f) = (-\infty,+\infty) $$

(b)$$ 5x+6 \neq 0 \\
      x \neq -\frac{6}{5} \\
      dom(f) = (-\infty,-\frac{6}{5}) \cup (-\frac{6}{5},+\infty)$$

(c)$$ x^2-5 \neq 0 \\
      x \neq \pm \sqrt{5} \\
      dom(f) = (-\infty,-\sqrt{5}) \cup (-\sqrt{5},\sqrt{5}) \cup (\sqrt{5},+\infty)$$

(d)$$ x^2-2x-3 \neq 0 \\
      (x-3)(x+1) \neq 0 \\
      x \neq -1 \ or \ x \neq 3 \\
      dom(f) = (-\infty,-1) \cup (-1,3) \cup (3,+\infty)$$

(e)$$ \left\{\begin{aligned}
2x-3 \geq 0 \\
2x-3 \neq 0 \\
\end{aligned}\right. \\
2x-3>0 \\
x > \frac{3}{2} \\
dom(f)=(\frac{3}{2},+\infty)$$

(f)$$ \left\{\begin{aligned}
1-2x \neq 0 \\
x+3 \geq 0 \\
\end{aligned}\right. \\
\left\{\begin{aligned}
x \neq \frac{1}{2} \\
x \geq -3 \\
\end{aligned}\right.\\
dom(f)=[-3,\frac{1}{2}) \cup (\frac{1}{2},+\infty)$$

(g)$$ \left\{\begin{aligned}
1-x^2 \neq 0 \\
2x+5 \geq 0 \\
\end{aligned}\right. \\
\left\{\begin{aligned}
x \neq \pm 1 \\
x \geq -\frac{5}{2} \\
\end{aligned}\right.\\
dom(f)=[-\frac{5}{2},-1) \cup (-1,1) \cup  (1,+\infty)$$

(h)$$ \left\{\begin{aligned}
x^2+3x-10 \neq 0 \\
x^2+3x-10 \geq 0 \\
\end{aligned}\right. \\
x^2+3x-10 > 0 \\
(x+5)(x-2) > 0 \\
x < -5 \ or \ x > 2 \\
dom(f)=(-\infty,-5) \cup (2,+\infty)$$

### Q2 {- #q2.2.2}
(Trang-Paige Tran a,c,e,g)

(a)$$ f(x)=y=x^2-5 \\
      x^2 = y+5 \\
      only \ if \ y+5 \geq 0, x = \pm \sqrt{y+5} \\
      we \ get \ y \geq -5 \\
      ran(f) = [-5,+\infty)$$
(b)This is a parabola with an upward opening, and the minimum value is :
$$  f(x) = x^2-2x-3 \\
         = (x-1)^2-4 $$ 
Thus the minimum value is -4, when x=1.
$$ ran(f) = [-4,+\infty)$$
(c)$$ f(x)=y=\frac{2}{5x+6} \\
      5x+6 = \frac{2}{y} \\
      5x = \frac{2}{y} - 6 \\
      x = \frac{2}{5y}-\frac{6}{5} \\
      x \ can \  be \  solved \ if \ and \ only \ if \ y \neq 0 \\
      ran(f) = (-\infty,0) \cup (0, +\infty)$$
(d)$$ f(x)=y=3-\frac{1}{2x-1} \\
      \frac{1}{2x-1} = 3-y \\
      2x-1 = \frac{1}{3-y} \\
      2x = \frac{1}{3-y}+1 \\
      x = \frac{1}{2(3-y)}+\frac{1}{2} \\
      x \ can \  be \  solved \ if \ and \ only \ if \ 2(3-y) \neq 0 \\
      y \neq 3 \\
      ran(f) = (-\infty,3) \cup (3, +\infty)$$
      
(e)$$ f(x)=y=\frac{1}{\sqrt{2x-3}} \\
      \sqrt{2x-3} = \frac{1}{y} \\
      only \ if \ y \geq 0, 2x-3 = \frac{1}{y^2} \\
      2x = \frac{1}{y^2}+3 \\
      x = \frac{1}{2y^2}+\frac{3}{2}\\
      x \ can \  be \  solved \ if \ and \ only \ if \ y \neq 0 \\
      Thus \ y>0 \\
      ran(f) = (0, +\infty)$$
(f)$$ f(x)=y=\frac{1}{x^2-5} \\
      x^2-5 = \frac{1}{y} \\
      x^2 = \frac{1}{y}+5 \\
      x = \pm \sqrt{\frac{1}{y}+5} \\
      x \ can \  be \  solved \ if \ and \ only \ if \ y \neq 0 \ and \ \frac{1}{y}+5 \geq 0\\
      y > 0 \ or \ y \leq -\frac{1}{5} \\
      ran(f) = (-\infty,-\frac{1}{5}] \cup (0, +\infty)$$     
(g)As in (b), $$f(x)=x^2-2x-3$$
we get $$ ran(f) = [-4,+\infty) $$
Suppose $$ h = x^2-2x-3, h \in [-4,+\infty) $$
Then we get 
$$ f(x)=y=\frac{1}{x^2-2x-3} = \frac{1}{h} \\
      h = \frac{1}{y} \\
      x \ can \  be \  solved \ if \ and \ only \ if \ y \neq 0 \\
      As \ h \in [-4,+\infty), \ Thus \  y > 0 \ or \ y \leq -\frac{1}{4} \\
      ran(f) = (-\infty,-\frac{1}{4}] \cup (0, +\infty)$$  
      
## Exercise 2.3 {- #q2.3}

### Q1 {- #q2.3.1}
(Ju-yeon Sally Choi)

$$ F(x,y)= 2x^2+3y^2-4 $$
As for x-intercepts, 
$$ y=0 \ and \ F(x,y)=0\\
   F(x,y) = 2x^2+3 \times 0^2 - 4 = 2x^2 - 4 = 0\\
   x^2 = 2\\
   x = \pm \sqrt{2}$$
Thus the x-intercepts are $$(-\sqrt{2},0) \ or \ (\sqrt{2},0) $$
As for y-intercepts, 
$$ x=0 \ and \ F(x,y)=0\\
   F(x,y) = 2 \times 0^2+3y^2 - 4 = 3y^2 - 4 = 0\\
   y^2 = \frac{4}{3}\\
   y = \pm \frac{2\sqrt{3}}{3}$$
Thus the x-intercepts are $$(0,-\frac{2\sqrt{3}}{3}) \ or \ (0,\frac{2\sqrt{3}}{3}) $$

### Q2 {- #q2.3.2}
(Ju-yeon Sally Choi)

$$ \left\{\begin{aligned}
0 = a \times 2^2 + b \times 2 + c \\
0 = a \times (-3)^2 + b \times (-3) + c \\
-6 = a \times 0^2 + b \times 0 + c \\
\end{aligned}\right. \\
\left\{\begin{aligned}
0 = 4a + 2b + c \\
0 = 9a - 3b + c \\
-6 = c \\
\end{aligned}\right. \\
\left\{\begin{aligned}
a = 1 \\
b = 1 \\
c = -6\\
\end{aligned}\right. \\$$

### Q3 {- #q2.3.3}
(Ju-yeon Sally Choi)

(a)As for x-intercepts, y = 0
$$ y = 0 = x^2+4x+5 $$
$$ b^2-4ac = 4^2-4 \times 1 \times5 = -4 < 0 $$
Thus the x-intercepts don't exist.

As for y-intercepts, x = 0
$$ y =0^2+4 \times 0 +5 = 5 $$
Thus the y-intercept is $$ (0,5) $$

(b)
```{r, echo=F}
y<-function(x) x^2+4*x+5

x = pretty(c(-5,5),3000)

plot(x,y(x),type = "l",xlab="x",ylab="y", ylim = c(-5,25) )
abline(v=0,lty=2)
abline(h=0,lty=2)
```

### Q4 {- #q2.3.4}
(Oyu Enkhbold)

(a)As $$ 2x+y-3=0 $$ 
We get $$ y = 3-2x $$
Putting into $$ x^2+y^2 =5$$
We get $$ x^2+(3-2x)^2 = 5 \\
          x^2 + 9 - 12x + 4x^2 -5 = 0 \\
          5x^2 - 12x +4 = 0\\
          (x-2)(5x-2)=0\\
          x =2 \ or \ x=\frac{2}{5}\\
          When \ x=2, \ y = -1 \\
          When \ x= \frac{2}{5}, \ y = \frac{11}{5}$$
Thus we get $$ L \cap C = \lbrace{ (2,-1),(\frac{2}{5},\frac{11}{5})}\rbrace $$

(b)As $$ 2x+y-3=0 $$ 
We get $$ y = 3-2x $$
Putting into $$ x^2+2y^2 =6$$
We get $$ x^2+2(3-2x)^2 = 6 \\
          x^2 + 18 - 24x + 8x^2 -6 = 0 \\
          9x^2 - 24x +12 = 0\\
          3x^2 - 8x +4 = 0\\
          (x-2)(3x-2)=0\\
          x =2 \ or \ x=\frac{2}{3}\\
          When \ x=2, \ y = -1 \\
          When \ x= \frac{2}{3}, \ y = \frac{5}{3}$$
Thus we get $$ L \cap E = \lbrace{ (2,-1),(\frac{2}{3},\frac{5}{3})}\rbrace $$

(c)As $$ x^2+y^2 =5 $$ 
We get $$ x^2 = 5-y^2 $$
Putting into $$ x^2+2y^2 =6$$
We get $$ (5-y^2)+2y^2 = 6 \\
          y^2=1\\
          y =1 \ or \ y=-1\\
          When \ y=1, \ x= \pm 2 \\
          When \ y= -1, \ x= \pm 2$$
Thus we get $$ C \cap E = \lbrace{ (2,1),(2,-1),(-2,1),(-2,-1)}\rbrace $$

### Q5 {- #q2.3.5}
(Oyu Enkhbold)

As $$ ax+y=2 $$ 
We get $$ y = 2-ax $$
Putting into $$ x^2+y^2 =1$$
We get $$ x^2+(2-ax)^2 = 1 \\
          x^2 + 4 - 4ax + a^2x^2 -1 = 0 \\
          (1+a^2)x^2 - 4ax +3 = 0$$
As there is only one element in the set, thus the equation only  has one solution.As for the linear equation in two unknowns, that is $$ b^2-4ac = 0 $$ then we can get 
$$  (-4a)^2 - 4 \times (1+a^2) \times 3 = 0 \\
   4a^2-12 = 0 \\
   a = \pm \sqrt{3}$$
Thus we get $$a = \pm \sqrt{3}$$

